\section*{References}
\addcontentsline{toc}{section}{References}
Abdelaziz, N \& El-Rabbany, A 2022, 'An Integrated INS/LiDAR SLAM Navigation System for GNSS-Challenging Environments', \textit{Sensors (Basel)}, vol. 22, no. 12, DOI:10.3390/s22124327

Agheli, M \& Nestinger, SS 2012, 'Study of the Foot Force Stability Margin for multi-legged/wheeled robots under dynamic situations', \textit{Proceedings of 2012 IEEE/ASME 8th IEEE/ASME International Conference on Mechatronic and Embedded Systems and Applications}, IEEE/ASME, Suzhou, China, pp. 99-104. 

Allouis, E, Blake, R, Gunes-Lasnet, S, Jorden, T, Maddison, B, Schroeven-Deceuninck, H, Stuttard, M, Truss, P, Ward, K, Ward, R, Woods, M 2013, 'A Facility for the Verification \& Validation of Robotics \& Autonomy for Planetary Exploration'

Anand, B, Patil, AG, Senapati, M, Barsaiyan, V \& Rajalakshmi, P 2020, 'Comparative Run Time Analysis of LiDAR Point Cloud Processing with GPU and CPU', in \textit{2020 IEEE International Conference on Computing, Power and Communcation Technologies}, IEEE, Greater Noida, India, pp. 650-654.

Asvadi, A, Premebida, C, Peixoto, P \& Nunes, U 2016, '3D Lidar-based static and moving obstacle detection in driving environments: An approach based on voxels and multi-region ground planes', \textit{Robotics and Autonomous Systems}, vol. 83, pp. 299-311, DOI:10.1016/j.robot.2016.06.007.

Atlassian n.d., \textit{The Agile Coach}, Atlassian, viewed 19 April 2023, \\ \textless https://www.atlassian.com/agile\textgreater.

Auat Cheein, FA, Lopez, N, Soria, CM, di Sciascio, FA, Lobo Pereira, FL \& Carelli, R 2010, 'SLAM algorithm applied to robotics assistance for navigation in unknown environments', \textit{Journal of NeuroEnginering and Rehabilitation}, vol. 7, DOI:10.1186/1743-0003-7-10.

Badue, C, Guidolini, R, Carneiro, RV, Azevedo, P, Cardoso, VB, Forechi, A, Jesus, L, Berriel, R, Paixão, TM, Mutz, F, Veronese, L, Oliveira-Santos, T \& De Souza, AF 2021, 'Self-driving cars: A survey', \textit{Expert Systems with Applications}, vol. 165, DOI:10.1016/j.eswa.2020.113816.

Bartsch, S, Birnschein, T, Langosz, M, Hilljegerdes, J, Kuehn, D \& Kirchner, F 2012, 'Development of the Six-Legged Walking and Climbing SpaceClimber', \textit{Journal of Field Robotics}, vol. 29, no. 3, pp. 506-532, DOI:10.1002/rob.21418.

Bereczky, N, Duch, A, Németh, K \& Roura, S 2016, 'Quad-kd trees: A general framework for kd trees and quad trees', \textit{Theoretical Computer Science}, vol. 616, pp. 126-140.

Bichuette, ME \& Trajano, E 2018, 'Diversity of Potamolithus (Littorinimorpha, Truncatelloidea) in a high-diversity spot for troglobites in southeastern Brazil: role of habitat fragmentation in the origin of subterranean fauna, and conservation status', \textit{Subterranean Biology}, vol. 25, pp. 61-88, DOI:10.3897/subtbiol.25.23778.

Bright, H, Mahony, T, Verboon, N \& Zilm, L 2022, ’CaveX Final Report’, Honours thesis, The University of
Adelaide.

Capterra 2023, GIS Software DroneDeploy, viewed 28 May 2023, \\ \textless https://www.capterra.com.au/software/197016/dronedeploy\textgreater.

Chen, Z, Liu, J \& Gao, F 2022, 'Real-time gait planning method for six-legged robots to optimize the performances of terrain adaptability and walking speed', \textit{Mechanism and Machine Theory}, vol. 168, DOI:10.1016/j.mechmachtheory.2021.104545.

Cooper, J, King, M, Natt, C, Lee, H \& Thomas, A 2021, 'CaveX Honours Final Report', Honours thesis, The
University of Adelaide.

CSIRO Robotics 2020, \textit{csiro-robotics/syropod\_remote}, GitHub, viewed 28 May 2023, \\ \textless https://github.com/csiro-robotics/syropod\_remote/tree/master\textgreater.

CSIRO Robotics 2021, \textit{csiro-robotics/syropod\_highlevel\_controller: OpenSHC: A Versatile Multilegged Robot Controller}, GitHub, viewed 28 May 2023, \\ \textless https://github.com/csiro-robotics/syropod\_highlevel\_controller/tree/master\textgreater.

DigiKey n.d., \textit{114992687 Seeed Technology Co., Ltd $\mid$ Fans, Thermal Management $\mid$ DigiKey}, DigiKey, viewed 26 May 2023, \textless https://www.digikey.com.au/en/products/detail/seeed-technology-co-ltd/114992687/14552876\textgreater.

DroneDeploy 2022, \textit{3D Point Clouds - DroneDeploy}, DroneDeploy, viewed 27 May 2023, \\ \textless https://help.dronedeploy.com/hc/en-us/articles/1500004860641-3D-Point-Clouds\textgreater.

DroneDeploy n.d.a, \textit{ROS - Docs}, DroneDeploy, viewed 27 May 2023, \\ \textless https://docs-automate.dronedeploy.com/docs/ros\textgreater.

DroneDeploy n.d.b, \textit{Key features - Docs}, DroneDeploy, viewed 27 May 2023, \\ \textless https://docs-automate.dronedeploy.com/docs/rocos-for-ros-robots\textgreater.

DroneDeploy n.d.c, \textit{Examples - Docs}, DroneDeploy, viewed 27 May 2023, \\ \textless https://docs-automate.dronedeploy.com/docs/examples\textgreater.

Dualsky 2022, \textit{Xpower HED series}, Dualsky, viewed 21 May 2023. \\ \textless http://en.dualsky.com/Xpower\_LiPos/64986f2b-c65ed53c-
6f56-99e22ad8c108.shtml.\textgreater

Dubowsky, S, Iagnemma, K, Liberatore, S, Lambeth, DM, Plante, JS \& Boston, PJ 2005, 'A Concept Mission: Microbots for Large-Scale Planetary Surface and Subsurface Exploration', in \textit{AIP Conference Proceedings}, AIP, Canberra, Australia, pp. 1449-1458.

Guo, M, Zhang, L, Liu, X, Du, Z, Song, J, Liu, M, Wu, X \& Huo, X 2021, '3D Lidar SLAM Based on Ground Segmentation and Scan Context Loop Detection', in \textit{11th IEEE Annual International Conference on CYBER Technology in Automation, Control, and Intelligent Systems (CYBER)}, IEEE, Jiaxing, China, pp. 692-697.

Jin, J, Zhang, Y, Zhou, Z, Jin, M, Yang, X \& Hu, F 2023, 'Conflict-based search with D* lite algorithm for robot path planning in unknown dynamic environments', \textit{Computers and Electrical Engineering}, vol. 105, DOI:10.1016/j.compeleceng.2022.108473.

Kambesis, P 2009, ’The importance of cave exploration to scientific research’, \textit{Journal of Cave and Karst Studies}, vol. 69, no. 1, pp. 46-58.

Karam, S, Lehtola, V \& Vosselman, G 2021, 'Simple loop closing for continuous 6DOF LIDAR\&IMU graph SLAM with planar features for indoor environments', \textit{ISPRS Journal of Photogrammetry and Remote Sensing}, vol. 181, pp. 413-426, DOI:10.1016/j.isprsjprs.2021.09.020.

Khatib, O 1986, 'Real-Time Obstacle Avoidance for Manipulators and Mobile Robots', \textit{The International Journal of Robotics Research}, vol. 5, no. 1, pp. 90-98.

Kim, P, Chen, J, Kim, J \& Cho, Y 2018, 'SLAM-Driven Intelligent Autonomous Mobile Robot Navigation for Construction Applications', in \textit{25th Workshop of the European Group for Intelligent Computing in Engineering}, EG-ICE, Lausanne, Switzerland, pp. 254-269.

LaValle, SM \& Kuffner, JJ 2001, 'Randomized Kynodynamic Planning', \textit{The International Journal of Robotics Research}, vol. 20, no. 5, pp. 378-400.

Le, J, Pengcheng, Z, Wei, D, Jiayuan, L, Mingyao, A, Xuan, W \& Qingwu, H 2018, 'An Eight-Direction Scanning Detection Algorithm for the Mapping Robot Pathfinding in Unknown Indoor Environment', \textit{Sensors}, vol. 18, no. 12, DOI:10.3390/s18124254.

Lele, AS, Fang, Y, Ting, J \& Raychowdhury, A 2020, 'Learning to Walk: Spike Based Reinforcement Learning for Hexapod Robot Central Pattern Generation', \textit{2020 2nd IEEE International Conference on Artificial Intellgence Circuits and Systems (AICAS)}, IEEE, Genova, Italy, pp. 208-212. 

Lewis, I 2019, ’South Australian geology and the State Heritage Register: an example of geoconservation of the Naracoorte Caves complex and karst environment’, \textit{Australian Journal of Earth Sciences}, vol. 66, no. 6, pp. 785–792.

Mur-Artal, R, Montiel, JMM \& Tardós, JD 2015, 'ORB-SLAM: A Versatile and Accurate Monocular SLAM System', \textit{IEEE Transactions on Robotics}, vol. 31, no. 5, pp. 1147-1163, DOI:10.1109/TRO.2015.2463671.

National Park Service (NPS) 2015, \textit{How Stalactites and Stalagmites Form}, U.S. Department of the Interior, viewed 21 May 2023, \\ \textless https://www.nps.gov/ozar/learn/education/speleothems.htm\textgreater.

Novak, R, Hrovat, A, Bedform, MD \& Javornik, T 2021, 'Geometric Simplifications of Natural Caves in Ray-Tracing-Based Propagation Modelling', \textit{Electronics}, vol. 10, no. 23, \\DOI:10.3390/electronics10232914.

NVIDIA n.d.a, \textit{Jetson Developer Tools $\mid$ NVIDIA Developer}, NVIDIA Developer, viewed 26 May 2023, \textless https://developer.nvidia.com/embedded/develop/tools\textgreater.

NVIDIA n.d.b, \textit{}, NVIDIA, viewed 26 May 2023, \textless https://www.nvidia.com/en-au/autonomous-machines/embedded-systems/jetson-nano-developer-kit/\textgreater.

Qi, CR, Su, H, Mo, K \& Guibas, LJ 2017, 'PointNet: Learning on Point Sets for 3D Classification and Segmentation', in \textit{2017 IEEE Conference on Computer Vision and Pattern Recognition (CVPR)}, IEEE, Honolulu, Hawaii, pp. 652-660.

Qin, T \& Cao, S 2019, \textit{GitHub - HKUST-Aerial-Robotics/A-LOAM: Advanced implementation of LOAM}, GitHub, viewed 25 March 2023, \textless https://github.com/HKUST-Aerial-Robotics/A-LOAM \textgreater.

Robotis 2023a, \textit{2XC430-W250}, Robotis, viewed 26 May 2023, \\ \textless https://emanual.robotis.com/docs/en/dxl/x/2xc430-w250/\textgreater.

Robotis 2023b, \textit{XC430-W240-T}, Robotis, viewed 26 May 2023, \\ \textless https://emanual.robotis.com/docs/en/dxl/x/xc430-w240/\textgreater.

ROS Wiki 2017, \textit{rosnodejs - ROS Wiki}, ROS Wiki, viewed 27 May 2023, \\ \textless https://wiki.ros.org/rosnodejs\textgreater.

ROS Wiki 2019a, \textit{Packages - ROS Wiki}, ROS Wiki, viewed 28 May 2023, \\ \textless https://wiki.ros.org/Packages\textgreater.

ROS Wiki 2019b, \textit{Topics - ROS Wiki}, ROS Wiki, viewed 28 May 2023, \\ \textless http://wiki.ros.org/Topics\textgreater.

ROS Wiki 2022, \textit{ROS/Tutorials/UnderstandingNodes - ROS Wiki}, ROS Wiki, viewed 28 May 2023, \\ \textless https://wiki.ros.org/ROS/Tutorials/UnderstandingNodes\textgreater.

Seeed Studio n.d., \textit{J401-datasheet.pdf}, Seeed Studio, viewed 26 May 2023, \\ \textless https://files.seeedstudio.com/wiki/reComputer-J4012/Carrier-Board-J401/J401-datasheet.pdf\textgreater.

Seekhao, N, Yu, G, Yuen, S, JaJa, J, Mongeau, L \& Li-Jessen NYK 2019, 'High-Performance Host-Device Scheduling and Data-Transfer Minimization Techniques for Visualization of 3D Agent-Based Wound Healing Applications', \textit{PDPTA}, vol. 19, pp. 69-76.

Shan, T \& Englot, B 2018, 'LeGO-LOAM: Lightweight and Ground-Optimized Lidar Odometry and Mapping on Variable Terrain', in \textit{2018 IEEE/RSJ International Conference on Intelligent Robots and Systems}, IEEE, Madrid, Spain, pp. 4758-4765.

Shang, E, An, X, Wu, T, Hu, T, Yuan, Q \& He, H 2015, 'LiDAR Based Negative Obstacle Detection for Field Autonomous Land Vehicles', \textit{Journal of Field Robotics}, vol. 33, no. 5, pp. 591-617, DOI:10.1002/rob.21609.

Tam, B, Talbot, F, Steindl, R, Elfes, A \& Kottege, N 2020, 'OpenSHC: A Versatile Multilegged Robot Controller', \textit{IEEE Access}, vol. 8, pp. 188908-188926, DOI:10.1109/ACCESS.2020.3031019.

Velodyne 2019, \textit{VLP-16 User Manual}, Velodyne LiDAR, viewed 28 May 2023, \\ \textless https://velodynelidar.com/wp-content/uploads/2019/12/63-9243-Rev-E-VLP-16-User-Manu\\al.pdf\textgreater.

Wang, H, Wang, C, Chen, L \& Xie, L 2021, 'F-LOAM: Fast LiDAR Odometry and Mapping', in \textit{2021 IEEE/RSJ International Conference on Intelligent Robots and Systems}, IEEE, Prague, Czech Republic, pp. 4390-4396.

Wang, Y \& Li, X 2021, 'An improved robust EKF algorithm based on sigma points for UWB and foot-mounted IMU fusion positioning', \textit{Journal of Spatial Science}, vol. 66, no. 2, pp. 329-350, DOI:10.1080/14498596.2019.1632754.

Williams, C 2021, \textit{Interview}, The University of Adelaide North Terrace Campus, 23 March.

Xiao, J, Ji, Q, Shen, Q, Jiang, J, Huang, Y \& Lou, J 2022, 'Accelerating stochastic-based reliability estimation for combinational circuits at RTL using GPU parallel computing', \textit{International Journal of Intelligent Systems}, vol. 37, no. 11, pp. 8309-8326, DOI:10.1002/int.22940.

Yadav, N \& Bleakley, C 2016, 'Fast calibration of a 9-DOF IMU using a 3 DOF position tracker and a semi-random motion sequence', \textit{Measurement}, vol. 90, pp. 192-198.

Yan, Y, Mao, Y \& Li, B 2018, 'SECOND: Sparsely Embedded Convolutional Detection', \textit{Sensors}, vol. 18, no. 10, DOI:10.3390/s18103337.

Yang, W, Wang, G \& Shen, Y 2020, 'Perception-Aware Path Finding and Following of Snake Robot in Unknown Environment', in \textit{2020 IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS)}, IEEE, Las Vegas, USA, pp. 5925-5930.

Zangrandi, M, Arrigoni, S \& Braghin, F 2021, \textit{Control of a Hexapod Robot Considering Terrain Interaction}, arXiv, viewed 15 May 2023, \textless https://arxiv.org/pdf/2112.10206.pdf\textgreater.

Zhang, J \& Singh, S 2014, 'LOAM: Lidar Odometry and Mapping in Real-time', in D Fox, LE Kavraki \& H Kurniawati, \textit{Robotics: Science and Systems}, Robotics Science and Systems, Berkeley, California, USA.

Zou, Q. Sun, Q, Chen, L, Nie, B \& Li, Q 2022, A Comparative Analysis of LiDAR SLAM-Based
Indoor Navigation for Autonomous Vehicles, IEEE Transactions on Intelligent Transportation
Systems, vol 23, no. 7, pp. 6907-6921. DOI:10.1109/TITS.2021.3063477.